---
title: "Code Book"
author: "nate_olson"
date: "June 21, 2014"
output: html_document
---

This is a description of the variables, data, and transformations performed to clean up the activity data from [http://archive.ics.uci.edu/ml/datasets/Human+Activity+Recognition+Using+Smartphones](http://archive.ics.uci.edu/ml/datasets/Human+Activity+Recognition+Using+Smartphones)

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(xtable)
data <- read.csv("HAR_summarized_tidydata.txt")
```


## Variables
```{r, echo=FALSE, message=FALSE, warning=FALSE}
Variables <- colnames(data)
Description <- c("Subject who performed the activity for each window sample. Its range is from 1 to 30. ","Type of activity performed while the measurements were acquired","Description of accelerometer vector measurement","statistical summary of the feature", "mean value")
data_table <- xtable(data.frame(Variables, Description))
```
```{r, results='asis', echo=FALSE}
print.xtable(data_table, type = "html",include.rownames = F)
```

## Data
The data represent data collected from the accelerometers from the Samsung Galaxy S smartphone.  This data can used to develop algorithms for classifying an activity based on accelerometer measurements.

## Transformations
The data set generated by `run_analysis.R` combines the test and training data sets then presents a summary in the form of the average value of the mean and standard deviation of the different accelerometer measurements for each subject and activity.


#### Additional Notes
This document was created using Rmarkdown where the variables were generated from the input data files.
